Marlowe: implementing and analysing financial contracts\thanks{Supported by IOHK.}

### 2019-12-05 papers/marlowe2019/paper.tex
Add timeout closure property to paper

\subsubsection{Money preservation}

@@

This requires that money is preserved (not created nor destroyed). We state this property as follows:

@@

>>>>

\subsubsection{Money preservation and contract timeout}

@@

To ensure this is the case we proved two properties:

\paragraph{Money preservation}
Money is not created or destroyed by the semantics. We state this property as follows:

@@

\paragraph{Timeout closes a contract}

For every Marlowe \texttt{Contract} there exists a slot number after which an empty transaction can be issued that will close the contract and refund all the money in its accounts.

A conservative upper bound for the expiration slot number can be calculated efficiently by using the function \texttt{maxTime} (or \texttt{maxTimeContract} in the Isabelle semantics).

We proved that this conservative upper bound works for every contract in a property stated as follows:

\begin{verbatim}
theorem timedOutTransaction_closes_contract :
  "validAndPositive_state sta
   ==> iniSlot >= minSlot sta
   ==> iniSlot >= maxTimeContract cont
   ==> endSlot >= iniSlot
   ==> accounts sta ~= []
   ==> isClosedAndEmpty
          (computeTransaction (| interval = (iniSlot, endSlot)
                               , inputs = [] |) sta cont)"
\end{verbatim}

\noindent

where \texttt{isClosedAndEmpty} is defined as follows:

\begin{verbatim}
fun isClosedAndEmpty :: "TransactionOutput => bool" where
"isClosedAndEmpty (TransactionOutput txOut) =
   (txOutContract txOut = Close
      /\ accounts (txOutState txOut) = [])" |
"isClosedAndEmpty _ = False"
\end{verbatim}

Because the money is preserved and we know that there is an empty transaction that can be sent at any point after \texttt{maxTime} that will empty the accounts of the contract: we know that money will not be locked in the contract forever.
